Community Detection Methods for the Generalized Random Dot Product Graph Model

### 2021-05-17 proposal/slides.Rmd
updated slides

* Preliminaries
  * Block Models and Community Detection
  * (Generalized) Random Dot Product Graphs
* Connecting Block Models to (G)RDPG Models
  * Popularity Adjusted Block Model
  * Subspace Clustering
* Community Detection in the (G)RDPG

@@

# Generalizations to Community Detection for the (G)RDPG

@@

$\forall a \in (0, 1)$, $\delta \in (0, 1)$, and $K \geq 2$, 
$\exists N(a, \delta, K) < \infty$ such that when $\min_k n_k \geq N$, 
with probability at least $1 - \delta$,

1. Single linkage clustering will produce perfect community detection.
2. An $\epsilon$-neighborhood graph with $\epsilon \in (0, a)$ will consist of 
at least $K$ disjoint subgraphs such that no subgraph contains members of two 
different communities.

@@

Then $\forall a \in (0, 1)$, $\delta \in (0, 1)$, $K \geq 2$, and $\xi \leq a / 3$, 
$\exists N(a, \delta, K, \xi) < \infty$ such that when $\min_k n_k \geq N$, 
with probability at least $1 - \delta$,

1. Single linkage will produce perfect community detection.
2. An $\epsilon$-neighborhood graph will consist of at least $K$ sub-graphs with no subgraph containing vertices of two communities.

This also holds for noisy points sampled on one-dimensional manifolds such that the manifolds are distance at least $a$ apart.

>>>>

* Preliminaries
  * Block Models and Community Detection
  * (Generalized) Random Dot Product Graphs
  * Connecting Block Models to the (G)RDPG
* The Popularity Adjusted Block Model
  * Connecting the PABM to the GRDPG
  * Subspace Clustering
* Community Detection for the (G)RDPG

@@

# General Community Detection for the (G)RDPG

@@

Then $\forall a \in (0, 1)$, $\delta \in (0, 1)$, and $K \geq 2$, 
$\exists N(a, \delta, K) < \infty$ such that when $\min_k n_k \geq N$, 
with probability at least $1 - \delta$,

1. Single linkage clustering will produce perfect community detection.
2. An $\epsilon$-neighborhood graph with $\epsilon \leq a$ will consist of 
at least $K$ disjoint subgraphs such that no subgraph contains members of two 
different communities.

@@

Then $\forall a \in (0, 1)$, $\delta \in (0, 1)$, $K \geq 2$, $\xi \leq a / 3$, 
$\exists N(a, \delta, K, \xi) < \infty$ such that when $\min_k n_k \geq N$, 
with probability at least $1 - \delta$,

1. Single linkage will produce perfect community detection.
2. An $\epsilon$-neighborhood graph will consist of at least $K$ sub-graphs with no subgraph containing vertices from multiple communities.

This also holds for noisy points sampled from one-dimensional manifolds such that the manifolds are distance at least $a$ apart.
